\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2019-07-29 analysis/paper/paper.Rmd
Added table of existing work for smooth hazard and variable selection

---
documentclass: jss
author:
  - name: Sahir Bhatnagar *
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mail.mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon *
    affiliation: University of Manitoba
    address: >
      318 Machray Hall
      Winnipeg, MB, Canada R3T 2N2
    email: \email{max.turgeon@umanitoba.ca}
    url: http://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James Hanley
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title:
  formatted: "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
  # If you use tex in the formatted title, also supply version without
  plain:     "casebase: An Alternative Framework For Survival Analysis"
  # For running headers, if needed
  short:     "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
abstract: >
  The abstract of the article. * joint co-authors
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{Java}"]
  plain:     [keywords, not capitalized, Java]
preamble: >
  \usepackage{amsmath}
  \usepackage{longtable}
output: 
  rticles::jss_article:
    number_sections: TRUE     #added argument option 
    citation_package: "natbib"  #All my citations use biblatex, not natbib. 
biblio-style: jss      #Listed to use in JSS Instructions for Authors, but not in template by default. 
bibliography: references.bib  #Also not included in template by default. 
fig_width: 7
fig_height: 6
fig_caption: true
---

@@

\begin{table}
  \begin{tabular}{p{1.8in}lll}
\hline
    &  Parameters &  Density \proglang{R} function & \code{dist}\\
    & {\footnotesize{(location in \code{\color{red}{red}})}} & & \\
\hline
    Exponential & \code{\color{red}{rate}}             & \code{dexp}   & \code{"exp"} \\
    Weibull (accelerated failure time)     & \code{shape, {\color{red}{scale}}}     & \code{dweibull} & \code{"weibull"} \\
    Weibull (proportional hazards)     & \code{shape, {\color{red}{scale}}}     & \code{dweibullPH} & \code{"weibullPH"} \\
    Gamma       & \code{shape, \color{red}{rate}}      & \code{dgamma} & \code{"gamma"}\\
    Log-normal  & \code{{\color{red}{meanlog}}, sdlog}   & \code{dlnorm} & \code{"lnorm"}\\
    Gompertz    & \code{shape, {\color{red}{rate}}}      & \code{dgompertz} & \code{"gompertz"} \\
    Log-logistic & \code{shape, {\color{red}{scale}}}   & \code{dllogis} & \code{"llogis"}\\
    Generalized gamma (Prentice 1975)   & \code{{\color{red}{mu}}, sigma, Q} & \code{dgengamma} & \code{"gengamma"} \\
    Generalized gamma (Stacy 1962)& \code{shape, {\color{red}{scale}}, k} & \code{dgengamma.orig} & \code{"gengamma.orig"} \\
    Generalized F     (stable)    & \code{{\color{red}{mu}}, sigma, Q, P} & \code{dgenf} & \code{"genf"} \\
    Generalized F     (original)  & \code{{\color{red}{mu}}, sigma, s1, s2} & \code{dgenf.orig} & \code{"genf.orig"} \\
\hline
  \end{tabular}
  \caption{Built-in parametric survival distributions in \pkg{flexsurv}.}
  \label{tab:dists}
\end{table}

>>>>

---
documentclass: jss
author:
  - name: Sahir Bhatnagar *
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{sahir.bhatnagar@mail.mcgill.ca}
    url: http://sahirbhatnagar.com/
  - name: Maxime Turgeon *
    affiliation: University of Manitoba
    address: >
      318 Machray Hall
      Winnipeg, MB, Canada R3T 2N2
    email: \email{max.turgeon@umanitoba.ca}
    url: http://maxturgeon.ca/
  - name: Jesse Islam 
    affiliation: McGill University
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{jesse.islam@mail.mcgill.ca}
  - name: James Hanley
    affiliation: McGill Univeristy
    address: >
      1020 Pine Avenue West
      Montreal, QC, Canada H3A 1A2
    email: \email{james.hanley@mcgill.ca}
    url: http://www.medicine.mcgill.ca/epidemiology/hanley/
  - name: Olli Saarela
    affiliation: University of Toronto
    address: >
      Dalla Lana School of Public Health, 
      155 College Street, 6th floor, 
      Toronto, Ontario 
      M5T 3M7, Canada
    email: \email{olli.saarela@utoronto.ca}
    url: http://individual.utoronto.ca/osaarela/
title:
  formatted: "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
  # If you use tex in the formatted title, also supply version without
  plain:     "casebase: An Alternative Framework For Survival Analysis"
  # For running headers, if needed
  short:     "\\pkg{casebase}: An Alternative Framework For Survival Analysis"
abstract: >
  The abstract of the article. * joint co-authors
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{Java}"]
  plain:     [keywords, not capitalized, Java]
preamble: >
  \usepackage{amsmath}
  \usepackage{longtable}
  \usepackage{booktabs}
output: 
  rticles::jss_article:
    number_sections: TRUE     #added argument option 
    citation_package: "natbib"  #All my citations use biblatex, not natbib. 
biblio-style: jss      #Listed to use in JSS Instructions for Authors, but not in template by default. 
bibliography: references.bib  #Also not included in template by default. 
fig_width: 7
fig_height: 6
fig_caption: true
---

@@

\begin{longtable}{lp{1in}p{2in}p{1.1in}}
%  \begin{tabular}{lp{1in}p{2in}p{1.1in}}
\hline
    Package &    documentation  & Type & Function Call\\
    % & {\footnotesize{(location in \code{\color{red}{red}})}} & & \\
\hline
    \href{https://cran.r-project.org/package=flexsurv}{flexsurv}  & \href{https://cran.r-project.org/web/packages/flexsurv/vignettes/flexsurv.pdf}{Vignette}, \href{https://www.jstatsoft.org/article/view/v070i08}{Jackson, C. JSS 2016}  & Fully-parametric. Also includes the spline model of Royston and Parmar (2002), in which both baseline survival and covariate effects can be arbitrarily flexible parametric functions of time. &   \texttt{flexsurvreg(Surv(recyrs, censrec) ~ group, data = bc, dist = "gengamma")}   \texttt{flexsurvspline(Surv(recyrs, censrec) ~ group, data = bc, k = 1, scale = "odds")}  \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \\
    \href{https://cran.r-project.org/package=AdapEnetClass}{AdapEnetClass}  & \href{https://link.springer.com/article/10.1007/s11222-015-9555-8}{Khan et al. Statistics and Computing 2016}  & Variable selection in AFT models using elastic net. No absolute risk estimates.    &   \texttt{cv.AWEnet(x, y, delta, weight=wt, lambda2=0.001, maxit=10, plot.it = T, AEnet=T)}  \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \\
    \href{https://cran.r-project.org/package=eha}{eha}  & \href{https://cran.r-project.org/web/packages/eha/vignettes/parametric.pdf}{Vignette}  & AFT model. Automatic produces plot of estimated smooth hazard function.    &   \texttt{phreg(Surv(enter + 40, exit + 40, event) ~ I(birthdate - 1810) + strata(ses), data = mort, dist = "gompertz")}  \\
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \\
    \href{https://cran.r-project.org/package=smoothSurv}{smoothSurv}  & \href{https://cran.r-project.org/web/packages/smoothSurv/smoothSurv.pdf}{R manual}  & An AFT model with an error distribution assumed to be a mixture of G-splines    &   \texttt{smoothSurvReg(surv ~ x1 * x2, logscale = ~1, info = FALSE, lambda = exp(2:(-1)))}  \\
\hline
%  \end{tabular}
  \caption{Built-in parametric survival distributions in \pkg{flexsurv}.}
  \label{tab:dists}
\end{longtable}

### 2019-07-29 analysis/paper/paper.tex
Added table of existing work for smooth hazard and variable selection

\Address{
    Sahir Bhatnagar *\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{sahir.bhatnagar@mail.mcgill.ca}\\
  URL: \url{http://sahirbhatnagar.com/}\\~\\
      Maxime Turgeon *\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{maxime.turgeon@mail.mcgill.ca}\\
  URL: \url{http://maxturgeon.ca/}\\~\\
      James Hanley\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{james.hanley@mcgill.ca}\\
  URL: \url{http://www.medicine.mcgill.ca/epidemiology/hanley/}\\~\\
      Olli Saarela\\
  University of Toronto\\
  Dalla Lana School of Public Health, 155 College Street, 6th floor,
  Toronto, Ontario M5T 3M7, Canada\\
  E-mail: \email{olli.saarela@utoronto.ca}\\
  URL: \url{http://individual.utoronto.ca/osaarela/}\\~\\
  }

@@

\usepackage{amsmath} \usepackage{longtable}

@@

This report was generated on 2019-07-22 17:17:57 using the following
computational environment and dependencies:

@@

#>  version  R version 3.6.0 (2019-04-26)

@@

#>  date     2019-07-22                  

@@

\begin{CodeOutput}
#> Local:    litreview /home/sahir/git_repositories/cbpaper
#> Head:     [38153a4] 2019-07-22: Update README.md
\end{CodeOutput}
\end{CodeChunk}

>>>>

\Address{
    Sahir Bhatnagar *\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{sahir.bhatnagar@mail.mcgill.ca}\\
  URL: \url{http://sahirbhatnagar.com/}\\~\\
      Maxime Turgeon *\\
  University of Manitoba\\
  318 Machray Hall Winnipeg, MB, Canada R3T 2N2\\
  E-mail: \email{max.turgeon@umanitoba.ca}\\
  URL: \url{http://maxturgeon.ca/}\\~\\
      Jesse Islam\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{jesse.islam@mail.mcgill.ca}\\

      James Hanley\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{james.hanley@mcgill.ca}\\
  URL: \url{http://www.medicine.mcgill.ca/epidemiology/hanley/}\\~\\
      Olli Saarela\\
  University of Toronto\\
  Dalla Lana School of Public Health, 155 College Street, 6th floor,
  Toronto, Ontario M5T 3M7, Canada\\
  E-mail: \email{olli.saarela@utoronto.ca}\\
  URL: \url{http://individual.utoronto.ca/osaarela/}\\~\\
  }

@@

\usepackage{amsmath} \usepackage{longtable} \usepackage{booktabs}

@@

This report was generated on 2019-07-29 10:55:18 using the following
computational environment and dependencies:

@@

#>  version  R version 3.6.1 (2019-07-05)

@@

#>  date     2019-07-29                  

@@

\begin{CodeOutput}
#> Local:    litreview-sahir /home/sahir/git_repositories/cbpaper
#> Remote:   litreview-sahir @ origin (https://github.com/sahirbhatnagar/cbpaper)
#> Head:     [c0cb26d] 2019-07-23: Merge pull request #6 from sahirbhatnagar/fixdocker
\end{CodeOutput}
\end{CodeChunk}
